{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-21 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, exciting changes

    \todoinline{Write this abstract when finishing. }
\end{abstract}

@@

@@

                \item Vassilis A., et al.: "Convergence rate of inertial Forward-Backward algorithm
                beyond Nesterov’s rule"

@@

            The following papers are related to stablizing, improving the acceleration scheme without monotone restarting. 

@@

    It is a single valued mapping and it has its domain on the entire $\RR^n$. 

@@

    \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq}, and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k := \alpha$ and $\rho_k := \rho$ for all $k \ge 0$.
        Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
        Then the constant R-WAPG sequence satisfies: 
        \begin{enumerate}
            \item $\rho = (1 - \mu/L\alpha^{-1})/(1 - \alpha)$. 
            \item $\theta = (1 - \alpha)(1 - \mu/L \alpha^{-1})/(1 - \mu/L)$. 
            \item For any $r \in \left(\sqrt{\mu/L}, \sqrt{L/\mu}\right)$, let $\alpha = r \sqrt{\mu/L}$. If $\sqrt{L/\mu} > r > 1$, then $\rho > 1$ else if $\sqrt{\mu/L} < r \le 1$ then $\rho \in (0, 1]$. 
            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = \left(1 - \sqrt{\mu/L}\right)/\left(1 + \sqrt{\mu/L}\right)$. 
        \end{enumerate}
    \end{lemma}
    \begin{proof}
        It's direct to show (i). 
        By the definition of $(\rho_k)_{k\ ge0}$ in the R-WAPG sequence definition, we have 
        \begin{align*}
            \rho_k &= 
            \frac{\alpha_{k + 1}^2 - \mu/L \alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2}
            = 
            \frac{\alpha^2 - \mu/L \alpha}{(1 - \alpha)\alpha^2}
            \\
            &= \frac{1 - (\mu/L)\alpha^{-1}}{1 - \alpha}. 
        \end{align*}
        To see (ii), it's direct by the definition of $\theta$: 
        \begin{align*}
            \theta &= 
            \frac{\rho \alpha(1 - \alpha)}{\rho \alpha^2 + \alpha} 
            = 
            (\rho \alpha)\frac{(1 - \alpha)}{\rho \alpha^2 + \alpha}
            \\
            &= \left(
                \frac{\alpha - (\mu/L)}{1 - \alpha}
            \right)\frac{(1 - \alpha)}{\alpha \frac{\alpha - \mu/L}{1 - \alpha} + \alpha}
            = \frac{\alpha - \mu/L}{\alpha\left(\frac{\alpha - \mu/L}{1 - \alpha}\right)+ \alpha}
            \\
            &= \left(1 - \mu/L \alpha^{-1}\right)\left(
                \frac{\alpha - \mu/L}{1 - \alpha} + 1
            \right)^{-1} 
            \\
            &= 
            \frac{(1 - \alpha)\left(1 - \mu/L \alpha^{-1}\right)}{1 - \mu/L}. 
        \end{align*}
        To see (iii), we substitute $\alpha = r \sqrt{\mu/L}$ into the expression for $\rho$ in (i) which gives: 
        \begin{align*}
            \rho_k &= \frac{1 - \mu/L\alpha^{-1}}{1 - \alpha} 
            = \frac{1 - r^{-1}\left(\mu/L\sqrt{L/\mu}\right)}{1 - r \sqrt{\mu/L}} 
            = \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}}. 
        \end{align*}
        If $\sqrt{L/\mu}> r > 1$ then $\rho > 1$ because 
        \begin{align*}
            \rho &= \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}} 
            > \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
        \end{align*}
        When $\sqrt{\mu/L} < r < 1$, it has 
        \begin{align*}
            0 < 1 - r^{-1}\sqrt{\mu/L} < \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r\sqrt{\mu/L}} = \rho < \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
        \end{align*}
        The first inequality used $r > \sqrt{\mu/L}$. 
        The third inequality used $r < 1$. 
        To see (iv), substitute $\alpha = \sqrt{\mu/L}$ for $\rho$.

@@

    \begin{theorem}[Fixed momentum FISTA]\label{thm:fixed-momentum-fista}

>>>>

    \todo{Write this abstract when finishing. }
\end{abstract}

@@

        Our results is based the assumption $F = f + g$ where $g:Q \rightarrow \bar\RR^n$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 

@@

                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm
                beyond Nesterov's rule"

@@

            The following papers are related to stabiling, improving the acceleration scheme without monotone restarting. 

@@

    It is a single-valued mapping, and it has its domain on the entire $\RR^n$. 

@@

    \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and assume $L > \mu > 0$.
        Define $q := \mu/L$. 
        Then $\forall r \in \left(\sqrt{q},\sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := r \sqrt{q}$. 
            \item Fix any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ then the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
            $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
            \item The momentum term in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ has:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$. 
            \item When $r = 1$, $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
            \item For all $r \in \left(1, \sqrt{q^{-1}}\right)$, $\rho > 1$; for all $r \in \left(\sqrt{q}, 1\right]$ $\rho \le 1$. 
            \item For all $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, $\max(\rho, 1)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}q\right)$. 
        To see (i), fix any $\sqrt{q} < r < \sqrt{q^{-1}}$, so
            r &\in \left(\sqrt{q}, \sqrt{q^{-1}}\right)
            r\sqrt{q} \in 
                q, 1
        Therefore, $\alpha_k \in (\mu/L, 1)$. 
        To see $\rho_k$, by definition it has 
            \rho_k &= \frac{\alpha_{k + 1}^2 - q \alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} 
            = \frac{\alpha^2 - q \alpha}{(1 - \alpha)\alpha^2} 
            &= \frac{1 - q\alpha^{-1}}{1 - \alpha}
            &= \frac{1 - q r^{-1}\sqrt{q^{-1}}}{1 - r \sqrt{q}}
            &= \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}} > 0. 
        Simple algebra can show (ii). 
        To start, we substitute the constant sequence $\alpha, \rho$ for $\alpha_k, \rho_k$ into the definition of $\theta$: 
            \theta &= \frac{\rho\alpha(1 - \alpha)}{\rho \alpha^2 + \alpha}
            = (\rho\alpha)\frac{1 - \alpha}{\rho \alpha^2 + \alpha} = \rho \frac{1 - \alpha}{\rho \alpha + 1}
            \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}
            (1 - r\sqrt{q})
                1 + r\sqrt{q}\frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}
            &= (1 - r^{-1} \sqrt{q})\left(
                1 + \frac{r \sqrt{q} - q}{1 - r \sqrt{q}}
            &= \left(1 - r^{-1} \sqrt{q}\right)\left(
                \frac{1 - q}{1 - r \sqrt{q}}
            \right)^{-1} = \frac{(1 - r^{-1}\sqrt{q})(1 - r \sqrt{q})}{1 - q}. 
        Now it's the perfect opportunity to show (iii) by substituting $r = 1$ which has 
            \theta &= \frac{(1 - \sqrt{q})^2}{1 - q}
            \frac{(1 - \sqrt{q})}{(1 - \sqrt{q})(1 + \sqrt{q})}
            = \frac{1 - \sqrt{q}}{1 + \sqrt{q}}. 
        Next for (iv), we determine when $\rho$ switches from $> 1$ to $ \le 1$. 
        For any $r \in \left(1, \sqrt{q^{-1}}\right)$, we show $\rho > 1$: 
            \rho &= \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}} 
            > \frac{1 - \sqrt{q}}{1 - r \sqrt{q}} > \frac{1 - \sqrt{q}}{1 - \sqrt{q}} = 1
        The first inequality comes from $r > 1 \iff -r^{-1} > -1$, the second inequality comes from $r > 1 \iff -r < 1$. 
        For any $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by 
            \rho &= \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}} 
            \le \frac{1 - \sqrt{q}}{1 - r \sqrt{q}} \le \frac{1 - \sqrt{q}}{1 - \sqrt{q}} = 1. 
        The first inequality comes from $-r^{-1} \le - 1$; the second inequality comes from $-r \ge -1$. 
        Finally, to show (v), we consider by cases: 
            \item[A:] When $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$ by (iii), meaning that $1 - r^{-1}\sqrt{q} > 1 - r \sqrt{q}$. $\rho > 1 \implies \max(\rho, 1) = \rho$ hence 
                    \max(\rho, 1)(1 - \alpha) &= \rho(1- \alpha)
                    = \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - r \sqrt{q}) = 1 - r^{-1}\sqrt{q}. 
                In this case, the larger one of the two values: $\left\lbrace1 - \rho^{-1}\sqrt{q}, 1 - r\sqrt{q}\right\rbrace$ is taken. 
            \item[B:] When $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by (iii); hence $1 - r^{-1}\sqrt{q} \le 1 - r \sqrt{q}$ and $\max(1,\rho) = 1$ therefore: 
                \max(1, \rho)(1 - \alpha) = (1 - \alpha) = 1 - r \sqrt{q}. 
            Once again, the larger one of the quantity: $1 - r \sqrt{q}$ among $\{1 - r^{-1}\sqrt{q}, 1 - r\sqrt{q}\}$ is taken. 
        Therefore, for all vales of $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ are completed by cases: (A), (B).
        The larger of the value among $\{1 - r \sqrt{q}, 1 - r^{-1}\sqrt{q}\}$ is always taken. 
        Therefore it has: 
            \max(1, \rho)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q}\right). 

@@

    \begin{theorem}[Fixed momentum FISTA]\label{thm:fixed-momentum-fista}
        Suppose a constant 
    \end{theorem}
